\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage[hidelinks]{hyperref}
    \usepackage[left=2cm, right=2cm, top=1.5cm, bottom=1.5cm]{geometry}
    \usepackage{longtable}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}

% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
    \vspace*{-40pt}

    

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Profile
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \vspace*{-2pt}
  \begin{center}
    {\Huge \scshape {Dehbi Kamal}}\\
    \vspace*{2pt}
    \ {Data Science, IA \& ML engineer}\\
    % \vspace*{2pt}
    % Seeking a final year internship (4-6 months) to apply my expertise in Data Science, AI, and Machine Learning in a challenging and innovative environment.\\
    % \vspace*{2pt}
    \href{mailto:kamaldehbi0114@gmail.com}{kamaldehbi0114@gmail.com} | \href{tel:+212 607136757}{+212 607136757}\\
    \vspace*{2pt}
    \textbf{\href{https://github.com/kamaLc73}{GitHub | }}\textbf{\href{https://www.linkedin.com/in/kamal-dehbi/}{Linkedin}}\\
  \end{center}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     Education
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \header{Education}
      \vspace{1mm}
      \textbf{ENSAM Rabat : École nationale supérieure d\textquotesingle{}Arts et Métiers}\hfill Rabat, Morocco\\
Engineering in Data Science, AI \textbar{} Integrated Class Preparatory. \hfill Sep 2021 - Jun 2026\\

\vspace{1mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     Experience
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \header{Experience}
      \vspace{1mm}

      \textbf{Digiteam Archytas Conseil}\textbf{ | Chatbot Development} \hfill Rabat, Morocco | Jul 2025 - Sep 2025\\
          \vspace{-1mm}
\begin{itemize} \itemsep -3pt
\item[] • Developed a chatbot for the Fairlynk platform using a RAG pipeline, Langchain with groq API Key.
\item[] • Supported multilingual questions in French, English, and Spanish.
\item[] • Built user interface using Streamlit, HTML, and CSS.
\end{itemize}
      \textbf{Bank Al-Maghrib (Dar Assikah)}\textbf{ | Backend Development} \hfill Sale, Morocco | Jul 2024 - Aug 2024\\
          \vspace{-1mm}
\begin{itemize} \itemsep -3pt
\item[] • Built a Flask API for license plate detection from images using a CNN model.
\item[] • Achieved 95\% accuracy on Moroccan plates.
\item[] • Designed PostgreSQL database schema using SQLAlchemy.
\item[] • Deployed the application using Docker containers.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Skills
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \header{Skills}
  \vspace{1mm}
  \begin{longtable}{p{4cm}p{12cm}}
  Programming Languages: & Python, Java, C, C++, R, Matlab, Scala, HTML, CSS, JavaScript \\
  Libraries/Frameworks: & TensorFlow, Keras, Scikit-learn, XGBoost, Pandas, NumPy, Matplotlib, Seaborn, Plotly, OpenCV, NLTK, Spacy, Streamlit, Apache Kafka, Hadoop, Hive, Pig, Sqoop, Spark, HBase, Flask, FastAPI, Java EE, React, Bootstrap, Jinja, SQLAlchemy \\
  Tools / Platforms: & Power BI, Google Looker Studio, Git, GitHub, Linux, Docker, VS Code \\
  Databases: & MySQL, PostgreSQL, SQLite, Oracle SQL, MongoDB, Neo4j \\
  \end{longtable}
  \vspace{0mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     Projects
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \header{Projects}
      \vspace{1mm}
      {\textbf{Earthquake Early Warning System}}\textbf{ | \href{https://github.com/kamaLc73/Seismic-GNSS-CNN}{Link}}\hfill{\sl Deep Learning, CNN, GNSS}\\
          \vspace{-1mm}
\begin{itemize} \itemsep -3pt
\item[] Designed CNN models using high-rate GNSS data to predict earthquake magnitude and fault lines with improved accuracy.
\end{itemize}
          \vspace*{0mm}
      {\textbf{Named Entity Recognition (NER)}}\textbf{ | \href{https://github.com/kamaLc73/NER\_project}{Link}}\hfill{\sl NLP, spaCy, HTML, CSS}\\
          \vspace{-1mm}
\begin{itemize} \itemsep -3pt
\item[] Developed an NLP model for named entity recognition to extract entities from medical and generic texts, improving data extraction accuracy.
\end{itemize}
          \vspace*{0mm}
      {\textbf{Medical Data Science Lab}}\textbf{ | \href{https://github.com/HAS1ELB/DataCarelytics}{Link}}\hfill{\sl Streamlit, Pandas, Numpy, Plotly, Scikit-Learn, LangChain}\\
          \vspace{-1mm}
\begin{itemize} \itemsep -3pt
\item[] Created interactive dashboards and visualizations for clinical datasets using Streamlit, enhancing data-driven decision making.
\end{itemize}
          \vspace*{0mm}
      {\textbf{ENSAM Alumni Tracking (LinkedIn/Facebook)}}\textbf{ | \href{https://github.com/kamaLc73/Data-Collect-LinkedIn-Profiles-}{Link}}\hfill{\sl Beautiful Soup, Selenium}\\
          \vspace{-1mm}
\begin{itemize} \itemsep -3pt
\item[] Developed web scraping tools to collect alumni data from LinkedIn and Facebook, performed data analysis, and built models to predict career paths.
\end{itemize}
          \vspace*{0mm}
      {\textbf{Real-Time Stream Processing with Apache Kafka}}\textbf{ | \href{https://github.com/kamaLc73/YOLO\_kafka}{Link}}\hfill{\sl Apache Kafka, Streamlit, YOLO}\\
          \vspace{-1mm}
\begin{itemize} \itemsep -3pt
\item[] Implemented a scalable real-time data streaming architecture using Apache Kafka to process images, videos, and text data streams.
\end{itemize}
          \vspace*{0mm}
      {\textbf{Brain Tumor Classification}}\textbf{ | \href{https://github.com/lidwaa/brain\_tumor\_classification}{Link}}\hfill{\sl Deep Learning, CNN}\\
          \vspace{-1mm}
\begin{itemize} \itemsep -3pt
\item[] Developed a CNN model to classify brain tumors as benign or malignant, achieving 98\% accuracy.
\end{itemize}
          \vspace*{0mm}
      {\textbf{Secure Document Management}}\textbf{ | \href{https://github.com/kamaLc73/Doc\_management\_jee}{Link}}\hfill{\sl Java JEE, MySQL}\\
          \vspace{-1mm}
\begin{itemize} \itemsep -3pt
\item[] Built a secure document management system for file storage, consultation, and downloads using Java JEE and MySQL.
\end{itemize}
          \vspace*{0mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      %
      %     Certifications
      %
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \header{Certifications}
      \vspace{1mm}
      • CCNA: Introduction to Networks - \textbf{\href{https://www.credly.com/badges/540e0c44-897a-4762-873b-7a01fbfb68ab/public\_url}{Cisco Networking Academy}}\\
\vspace*{0.5mm}
      • CS50x: Introduction to Computer Science - \textbf{\href{https://certificates.cs50.io/e4d5f24a-9711-490a-9c03-5ed9ba3f056e.pdf?size=letter}{Harvard University (edX)}}\\
\vspace*{0mm}



    \ 
    \end{document}